\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts
% Latin Modern
% Extension of CM text+math
\usepackage{lmodern} % math, rm, ss, tt
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[scr=boondoxo,frak=boondox,bb=boondox]{mathalfa}
%SetFonts

\title{Brief Article}
\author{The Author}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\section{Publications and Presentations}
\textbf{Peer Reviewed Journal Articles}
\begin{enumerate}
\item Macintosh, B., Graham, J. R., Ingraham, P., Konopacky, Q., Marois, C., Perrin, M., Poyneer, L., Bauman, B., Barman, T., Burrows, A. S., Cardwell, A., Chilcote, J., De Rosa, R. J., Dillon, D., Doyon, R., Dunn, J., Erikson, D., Fitzgerald, M. P., Gavel, D., Goodsell, S., Hartung, M., Hibon, P., Kalas, P., Larkin, J., Maire, J., Marchis, F., Marley, M. S., McBride, J., Millar-Blanchaer, M., Morzinski, K., Norton, A., Oppenheimer, B. R., Palmer, D., Patience, J., Pueyo, L., Rantakyro, F., Sadakuni, N., Saddlemyer, L., Savransky, D., Serio, A., Soummer, R., Sivaramakrishnan, A., Song, I., Thomas, S., Wallace, J. K., Wiktorowicz, S., and Wolff, S., \emph{First light of the Gemini Planet Imager}, Proceedings of the National Academy of Sciences, 2014.

\item Savransky, D., Thomas, S. J., Poyneer, L. A. and Macintosh, B. A., \emph{Computer vision applications for coronagraphic optical alignment and image processing}, Applied Optics, 52, 14, 2013.

\item Belbruno, E., Moro-Mart’n, A., Malhotra, R., and Savransky, D., \emph{Chaotic exchange of solid material between planetary systems: implications for lithopanspermia}, Astrobiology, 12,  8, 2012.

\item Savransky, D., Cady, E. and Kasdin, N. J., \emph{Parameter distributions of Keplerian orbits}, ApJ, 728, 66, 2011.

\item Savransky, D. and Kasdin, N. J., \emph{Simulation and analysis of sub-$\mu$as precision astrometric data for planet-finding}, ApJ, 721, 1559, 2010.

\item McConnochie, T. H., Bell III, J. F., Savransky, D., Wolff, M. J., Toigo, A. D., Wang, H., Richardson, M. I., and Christensen, P. R., \emph{THEMIS-VIS Observations of Clouds in the Martian Mesosphere: Altitudes, Wind Speeds, and Decameter-Scale Morphology}, Icarus, 210, 2, 2010.

\item Savransky D., Kasdin, N. J., and Cady, E. \emph{Analyzing the Designs of Planet-Finding Missions}, PASP, 122:401-419, 2010.

\item Bell III, J.F., Savransky, D., and Wolff, M.J. \emph{Chromaticity of the Martian Sky as Observed by the Mars Exploration Rover Pancam}, J. Geophys. Res.,111, E12S05, 2006.

\item McConnochie, T.H., J.F. Bell III, D. Savransky, et al., \emph{Calibration and In-Flight Performance of the Mars Odyssey THEMIS Visible Imaging Subsystem (VIS) Instrument}, J. Geophys. Res., 111, E06018, 2006.

\item Bell III, J.F., J.R. Joseph, J. Sohl-Dickstein, H. Arneson, M. Johnson, M. Lemmon, and D. Savransky, \emph{In-Flight Calibration of the Mars Exploration Rover Panoramic Camera Instrument}, J. Geophys. Res., 111, E02S03, 2006.
\end{enumerate}

\textbf{Invited Talks}
\begin{enumerate}
\item 08/27/2013 - \emph{Space mission design for exoplanet imaging}, SPIE Optics + Photonics 2013, San Diego, CA
\item 4/16/2013 - \emph{Imaging Exoplanets: Instrumentation, Survey Design, and the Future of Exoplanet Exploration}, Cornell University, Ithaca, NY
\item 12/13/2012 - \emph{Faint Signal Detection in Exoplanet Imaging}, UC Davis, Davis, CA 
\item 02/28/2012 - \emph{Detection Probabilities in the Presence of Speckle Nosie}, UC Berkeley, Berkeley, CA
\item 04/26/2011 - \emph{Probabilities in Planet Finding: Statistical Modeling for Exoplanet Studies}, Goddard Space Flight Center, Greenbelt, MA
\item 12/08/2010 - \emph{Mission Planning and Optimization}, Jet Propulsion Laboratory, Pasadena, CA
\item 11/30/2010 - \emph{Data Stream Integration for Modeling Exosystems}, American Museum of Natural History, New York, NY
\item  06/21/2010 - \emph{Stellar Reflex Astrometry Applications for Planet-Finding}, Space Telescope Science Institute, Baltimore, MA
\end{enumerate}

\textbf{Selected Conference Presentations and Papers}
\begin{enumerate}
\item Savransky, D., Thomas, S. J., Poyneer, L. A. and Macintosh, B. A., Sadakuni, N., Dillon, D., Goodsell, S. J., Hartung, M, Hibon, P., Rantakyr\"{o}, F., Cardwell, A., Serio, A., \emph{Automated alignment and on-sky performance of the Gemini planet imager coronagraph}, Proc. SPIE 9147, 914740-914740-11, 2014

\item Perrin, M. D., Maire, J., Ingraham, P., Savransky, D., Millar-Blanchaer, M., Wolff, S. G., Ruffio, J., Wang, J. J., Draper, Z. H., Sadakuni, N., \emph{Gemini planet imager observational calibrations I: Overview of the GPI data reduction pipeline}, Proc SPIE 9147, 91473J-91473J-13, 2014

\item Savransky, D., \emph{Space mission design for exoplanet imaging}, Proc. SPIE 8864, 886403, 2013.

\item  Savransky, D.,  Macintosh, B. A., Graham, J., and  Konopacky Q. M. \emph{Campaign Scheduling and Analysis for the Gemini Planet Imager}, Proceedings of the International Astronomical Union, 8, pp 68-69. doi:10.1017/S1743921313007916, 2013. 

\item Savransky, D., Macintosh, B. A., Konopacky, Q. M., Barman, T. S., and Marois, C., \emph{Wavelength-Diversity Derived Low Resolution Spectra of HR8799b}, AAS Meeting \#221, 2013.

\item Savransky, D. , Macintosh, B. A., Thomas, S., J.,  Poyneer, L. A.,  Palmer, D. W.,  De Rosa, R. J., and  Hartung, M., \emph{Focal plane wavefront sensing and control for ground-based imaging}, Proc. SPIE 8447, 84476S, 2012.

\item Kasdin, N. J., Lisman, D., Shaklan, S., Thomson, M., Cady, E., Martin, S., Marchen, L., Vanderbei, R. J., Macintosh, B., Rudd, R. E., Savransky, D., Miikula, J., and Lynch, D., \emph{Technology demonstration of starshade manufacturing for NASA's Exoplanet mission program}, Proc. SPIE 8442, 84420A, 2012.

\item Ammons, S. M., Bendek, E. A., Guyon, O., Macintosh, B. and Savransky, D., \emph{Theoretical limits on bright star astrometry with multi-conjugate adaptive optics using a diffractive pupil}, Proc. SPIE 8447, 84470P, 2012.

\item Savransky, D. and Kasdin, N. J., \emph{Optimal Estimation for Exoplanet Data Streams}, AAS Meeting \#217,  \#318.02, 2011

\item Savransky, D., Groff, T. D., Kasdin, N. J., \emph{Experimental Verification of Bayesian Planet Detection Algorithms with a Shaped Pupil Coronagraph}, In the Spirit of Lyot, 2010

\item Savransky, D., Spergel, D. N., Kasdin, N. J., Cady, E., Lisman, P. D., Pravdo, S. H., Shaklan, S. B., Fujii Y., \emph{Occulting Ozone Observatory science overview}, Proc. SPIE,  7731, 2010.

\item Savransky, D., Kasdin, N. J., \emph{Dynamic Filtering for the Analysis of Astrometric and Radial Velocity Data Sets for the Detection of Exoplanets}, AIAA Guidance, Navigation, and Control, 6083, 2009.

\item Savransky, D. and Kasdin, N. J. \emph{Design Reference Mission Construction for Planet Finders}, Proc. SPIE,  7010, 70101T, 2008.

\end{enumerate}

\end{document}  